A decomposition Approach for solving the JSP using multi-shot ASP\thanks{Supported by organization x.}

### 2022-01-27 ICLP Paper/samplepaper.tex
update 2nd table

Size & \multicolumn{3}{c}{$50\times15$} & \multicolumn{3}{c}{$50\times20$} & \multicolumn{3}{c}{$100\times20$}\\
Strategy & Makespan & Time & Ints & Makespan & Time & Ints & Makespan & Time & Ints % \\
    \midline% \hline\\[-2.75mm]
    J-EST            & $3524.8$ & $1000.0$   & $2.0$	   & $3540.8$      & $1000.0$ & $2.0$ & $6964.4$ & $1000.0$ & $4.0$\\ 
    J-MTWR            & $3456.2$  & $1000.0$   & $2.0$	& $3561.0$      & $1000.0$ & $2.0$ & $7149.6$ & $1000.0$ & $4.0$\\ 
    [1.5mm]
    M-EST             & $3083.8$  & $1000.0$   & $3.0$	& \boldmath{$3260.3$}      & $944.9$ & $3.5$ & $6031.9$ & $1000.0$ & $6.0$\\
    M-MTWR        & \boldmath{$3060.3$}  & $1000.0$   & $3.0$	& $3287.9$      & $986.1$ & $3.9$ & \boldmath{$5948.6$} & $1000.0$ & $7.0$\\ 
    [1.5mm]
    M-EST$^\text{\,dyn}$            & $3098.4$  & $1000.0$   & $3.0$	& $3309.5$     & $1000.0$ & $4.0$ & $6115.1$ & $1000.0$ & $7.0$% \\[1.5mm]

>>>>

Size & \multicolumn{3}{c}{$50\times15$} & \multicolumn{3}{c}{$50\times20$} & \multicolumn{3}{c}{$100\times20$}\\
Strategy & Makespan & Time & Ints & Makespan & Time & Ints & Makespan & Time & Ints % \\
    \midline% \hline\\[-2.75mm]
    J-EST            & $3524.8$ & $1000.0$   & $2.0$	   & $3540.8$      & $1000.0$ & $2.0$ & $6964.4$ & $1000.0$ & $4.0$\\ 
    J-MTWR            & $3456.2$  & $1000.0$   & $2.0$	& $3561.0$      & $1000.0$ & $2.0$ & $7149.6$ & $1000.0$ & $4.0$\\ 
    [1.5mm]
    M-EST             & $3083.8$  & $1000.0$   & $3.0$	& \boldmath{$3260.3$}      & $944.9$ & $3.5$ & $6031.9$ & $1000.0$ & $6.0$\\
    M-MTWR        & $3060.3$  & $1000.0$   & $3.0$	& $3287.9$      & $986.1$ & $3.9$ & \boldmath{$5948.6$} & $1000.0$ & $7.0$\\ 
    [1.5mm]
    M-EST$^\text{\,dyn}$            & $3098.4$  & $1000.0$   & $3.0$	& $3309.5$     & $1000.0$ & $4.0$ & $6115.1$ & $1000.0$ & $7.0$ \\
    M-MTWR$^\text{\,dyn}$            & \boldmath{$3041.6$}  & $1000.0$   & $3.0$	& $3287.0$     & $980.4$ & $3.9$ & $6167.3$ & $1000.0$ & $5.0$
